Secure Composition of Robust and Optimising Compilers

### 2023-06-14 popl/main.tex
Contribs and disclaimer

\begin{center}\small\it
	{In the following, we use syntax highlighting accessible to both colourblind and black \& white readers~\citep{patrignani2020use}. 
	Specifically, we use a $\src{blue}$, $\src{sans\text{-}serif}$ font for our $\src{source}$,
	a $\trg{red}$, $\trg{bold}$ font for our $\trg{intermediate}$, 
	and a $\obj{green}$, $\obj{teletype}$ font for our $\obj{target}$ language.
	}
\end{center}
\end{abstract}

@@

\begin{itemize}
  \item %
        %\Cref{sec:compprop} presents a formal framework to reason about compositions of security properties and demonstrate its usage with concrete examples:
        A formal framework to reason about the composition of security properties (\Cref{sec:compprop}).
        %Given a most general trace model, we define the trace-based security properties \gls{tms}, \gls{sms}, \gls{ms}, \gls{cct}, and their compositions.
        Using the framework, the ease for formal reasoning about security property compositions is demonstrated by instantiating it on \gls{tms}, \gls{sms}, and \gls{cct}, which are ultimately composed to \gls{ms} and a combination of \gls{ms} and \gls{cct}.
        %For each of these properties, we also give a monitor which runs on another trace model that excludes unneccessary information and show that their composition is behaviorally similar to the composition of the trace-based security properties.
        %This two-level approach enhances modularity: When working with the security properties, one only needs to reason about the corresponding monitor.
        %%% let's omit above sentences completely. why ramble about monitors in the introduction? this ain't about model checking

  \item
        \Cref{sec:compcomp} studies different forms of secure compiler compositions.
        Concretely, it investigates upper and lower compositions, as well as the sequential composition.
        A simple corollary of sequential composition is the ability to freely reorder compiler optimizations without compromising security.

  \item \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.

  \item Our key contributions are formalized in the Coq proof assistant.
        The formalization for the compilers are \emph{extractable}.
        That is, one can translate our Coq code to Ocaml and run them.
        Finally, in this paper, whenever definitions or proofs are done in Coq, we use the symbol \CoqSymbol.
\end{itemize}}

We now describe the other sections of the paper.
In \Cref{sec:background}, the paper establishes the notions of traces, (hyper-)properties, and robust preservation, while \Cref{sec:relwork} compares this work with others.
We conclude in \Cref{sec:concl} and give an outlook for future work.

\contribution{Open Source \& Technical Report} Our technical report and the Coq formalisation are
available as supplementary material and will be made available upon acceptance of this paper.

>>>>

\begin{center}\small\it
	{This paper uses syntax highlighting accessible to both colourblind and black \& white readers~\citep{patrignani2020use}.
	Specifically, it makes use of a $\src{blue}$, $\src{sans\text{-}serif}$ font for a $\src{source}$,
	a $\trg{red}$, $\trg{bold}$ font for an $\trg{intermediate}$,
	and a $\obj{green}$, $\obj{teletype}$ font for a $\obj{target}$ language.
	}
\end{center}
\end{abstract}

@@

\begin{itemize}
  \item %
        %\Cref{sec:compprop} presents a formal framework to reason about compositions of security properties and demonstrate its usage with concrete examples:
        A formal framework to reason about the composition of security properties (\Cref{sec:compprop}).
        %Given a most general trace model, we define the trace-based security properties \gls{tms}, \gls{sms}, \gls{ms}, \gls{cct}, and their compositions.
        Using the framework, the ease for formal reasoning with compositions of security properties is demonstrated by instantiating the framework on \gls{tms}, \gls{sms}, and \gls{cct}, which are ultimately composed to \gls{ms} and a combination of \gls{ms} and \gls{cct}.
        %For each of these properties, we also give a monitor which runs on another trace model that excludes unneccessary information and show that their composition is behaviorally similar to the composition of the trace-based security properties.
        %This two-level approach enhances modularity: When working with the security properties, one only needs to reason about the corresponding monitor.
        %%% let's omit above sentences completely. why ramble about monitors in the introduction? this ain't about model checking

  \item %
        %\Cref{sec:compcomp} studies different forms of secure compiler compositions.
        Foundational, theoretical work on different forms of compositions of secure compilers (\Cref{sec:compcomp}).
        %Concretely, it investigates upper and lower compositions, as well as the sequential composition.
        First, this paper proves theorems which state that a compiler with multiple input or output languages is secure as long as the compiler is composed of several secure passes with one input and one output language, respectively.
        Second, a theorem about the sequential composition of secure compilers is proven, which states that sequentially composing secure compilers is, again, secure with respect to the composition of the properties they preserve.
        %A simple corollary of sequential composition is the ability to freely reorder compiler optimizations without compromising security.

  \item %
        % \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        A case-study demonstrating the power of our formal framework (\Cref{sec:casestud}).
        %We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        To this end, a compilation chain of several passes is presented.
        %The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        The chain attains a combination of \gls{ms} and \gls{cct} by means of applying the theoretical work from the previous contribution on the individual, secure passes concerning \gls{tms}, \gls{sms}, and \gls{scct}, respectively.
        %As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        Furthermore, the chain entails two passes for \gls{ms}\MK{maybe patch when optimizing passes are done} that are optimizing: One performs a simple \gls{dce} and the other \gls{cf}.
        %This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.
        This demonstrates that the usage of the presented framework is both simpler and more expressive compared to one monolithic security proof of the whole compilation chain.

  \item Our key contributions are formalized in the Coq proof assistant.
        The practically relevant parts of the formalization are \emph{extractable}.
        That is, one can translate the Coq code to Ocaml and run the compilation chain from the previous contribution.
        Finally, in this paper, whenever definitions or proofs are done in Coq, we use the symbol \CoqSymbol.
\end{itemize}}

%In \Cref{sec:background}, the paper establishes the notions of traces, (hyper-)properties, and robust preservation, while \Cref{sec:relwork} compares this work with others.
For the other parts of the paper, the notions of security properties and secure compilers are introduced (\Cref{sec:background}).
%We conclude in \Cref{sec:concl} and give an outlook for future work.
The work presented in this paper is compared to others from the literature (\Cref{sec:relwork}) and there is a conclusion with an outlook for future work (\Cref{sec:concl}).

\contribution{Open Source \& Technical Report} Our technical report and the Coq formalisation are available as supplementary material.\MKin{cite/link}
